Meta-analysis of the Interoceptive Accuracy Scale (IAS) Structure and its Subjective Correlates

### 2025-02-12 analysis/study2.qmd
manuscript updated
started Internal reliability

```{r}
library(gt)

@@

### ICQ
```{r}

@@

```{r}
names(df7a)[str_detect(names(df7a), "NEO")]
names(df9)[str_detect(names(df9), "BFI_")]

data <- rbind(
  data,
  make_cor(df9, vars_intero, with = "BFI_AGREEABLENESS", component="Personality") |>
    mutate(var_Correlate = "Agreeableness"),
  make_cor(df9, vars_intero, with = "BFI_CONSCIENTIOUSNESS", component="Personality") |>
    mutate(var_Correlate = "Conscientiousness"),
  make_cor(df9, vars_intero, with = "BFI_NEUROTICISM", component="Personality") |>
    mutate(var_Correlate = "Neuroticism"),
  make_cor(df9, vars_intero, with = "BFI_OPENNESS", component="Personality") |>
    mutate(var_Correlate = "Openness"),
  make_cor(df9, vars_intero, with = "BFI_EXTROVERSION", component="Personality") |>
    mutate(var_Correlate = "Extraversion"),
  make_cor(df10a, vars_intero, with = "IPIP6_Agreeableness", component="Personality") |>
    mutate(var_Correlate = "Agreeableness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Conscientiousness", component="Personality") |>
    mutate(var_Correlate = "Conscientiousness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Neuroticism", component="Personality") |>
    mutate(var_Correlate = "Neuroticism"),
  make_cor(df10a, vars_intero, with = "IPIP6_Openness", component="Personality") |>
    mutate(var_Correlate = "Openness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Extraversion", component="Personality") |>
    mutate(var_Correlate = "Extraversion"),
  make_cor(df10a, vars_intero, with = "IPIP6_HonestyHumility", component="Personality") |>
    mutate(var_Correlate = "Honesty-Humility")
)
```

@@

@@

# Alexithymia
average_corr |>
  filter(Component == "Alexithymia") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))
#BPQ
average_corr |>
  filter(Component == "BPQ") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

#MAIA
average_corr |>
  filter(Component == "MAIA") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))
#ICQ
average_corr |>
  filter(Component == "ICQ") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))
#Mood
average_corr |>
  filter(Component == "Mood") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

>>>>

```{r}
#| output: false

library(gt)

@@

### ICQ

```{r}

@@

```{r}
names(df7a)[str_detect(names(df7a), "NEO")]
names(df9)[str_detect(names(df9), "BFI_")]
names(df10a)[str_detect(names(df10a), "IPIP6_")]

data <- rbind(
  data,
  make_cor(df7a, vars_intero, with = "NEO_FFI_SUMSCORE", component = "Personality") |>
      mutate(var_Correlate = "Neuroticism"),
  make_cor(df9, vars_intero, with = "BFI_AGREEABLENESS", component="Personality") |>
    mutate(var_Correlate = "Agreeableness"),
  make_cor(df9, vars_intero, with = "BFI_CONSCIENTIOUSNESS", component="Personality") |>
    mutate(var_Correlate = "Conscientiousness"),
  make_cor(df9, vars_intero, with = "BFI_NEUROTICISM", component="Personality") |>
    mutate(var_Correlate = "Neuroticism"),
  make_cor(df9, vars_intero, with = "BFI_OPENNESS", component="Personality") |>
    mutate(var_Correlate = "Openness"),
  make_cor(df9, vars_intero, with = "BFI_EXTROVERSION", component="Personality") |>
    mutate(var_Correlate = "Extraversion"),
  make_cor(df10a, vars_intero, with = "IPIP6_Agreeableness", component="Personality") |>
    mutate(var_Correlate = "Agreeableness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Conscientiousness", component="Personality") |>
    mutate(var_Correlate = "Conscientiousness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Neuroticism", component="Personality") |>
    mutate(var_Correlate = "Neuroticism"),
  make_cor(df10a, vars_intero, with = "IPIP6_Openness", component="Personality") |>
    mutate(var_Correlate = "Openness"),
  make_cor(df10a, vars_intero, with = "IPIP6_Extraversion", component="Personality") |>
    mutate(var_Correlate = "Extraversion"),
  make_cor(df10a, vars_intero, with = "IPIP6_HonestyHumility", component="Personality") |>
    mutate(var_Correlate = "Honesty-Humility")
)
```

@@

## Internal Reliability

- sample df7c does not have individual BPQ items

```{r}

# BPQ 46 Items SV
df2_BPQ <- df2 |> select(contains("BPQ ")) 
df3_BPQ <- df3 |> select(contains("BPQ"), -contains("BPQ_"))

# BPQ 26 items - awareness subscale

df4_BPQ_A <- df4 |> select(contains("BPQ_"))

# BPQ 12 items VSF
df7a_BPQVSF <- df7b |> select(contains("BPQ_"), -BPQ_Sum)
df8a_BPQVSF <- df8a |> select(contains("BPQ"), -BPQ_A)

@@

average_corr |>
  filter(Component == "Alexithymia") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "BPQ") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "MAIA") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "ICQ") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Mood") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Maladaptive") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Schizotypic") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Autistic") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "Personality") |>
  group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

average_corr |>
  filter(Component == "World Beliefs") |>
  # group_by(var_Correlate) |>
  summarise(min = min(mean_r),
             max = max(mean_r))

### 2025-02-12 paper/1_Initial/manuscript.qmd
started Internal reliability

<!-- BPQ -->
The studies within our sample used the Body Perception Questionnaire short-form (BPQ-SF) and the very-short form (BPQ-VSF) to assess interoception [@cabrera2018assessing]. 
The BPQ-SF comprised of 46 items on a 5-point Likert scale assessing body awareness (26 items) and autonomic reactivity (21 items). 
The BPQ-VSF comprises of 12 items from the body awareness subscale of the BPQ-SF.
In this study, all scores assessing these two dimensions were grouped together, hence no disitintion is made between awareness measured with the BPQ-SF and the BPQ-VSF.

>>>>

<!-- BPQ -->
The studies within our sample used the Body Perception Questionnaire short-form (BPQ-SF) and the very-short form (BPQ-VSF) to assess interoception [@cabrera2018assessing]. 
The BPQ-SF comprised of 46 items on a 5-point Likert scale assessing body awareness (26 items) and autonomic reactivity (21 items). 
The BPQ-VSF comprises of 12 items from the body awareness subscale of the BPQ-SF.
In this study, all scores assessing these two dimensions were grouped together, hence no disitintion is made between awareness measured with the BPQ-SF and the BPQ-VSF, or eith scores obtained only using the awareness subscale.
